A Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-03-15 analysis/article.Rmd
fix: co2eq calculation

```{r benchmark-plot, fig.cap = "Benchmark results of machine learning algorithms."}
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)
autoplot(r) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

@@

```{r co2e}
tdp <- c(
    ## brain/batch Intel(R) Xeon(R) CPU E5-2650 v4 @ 2.20GHz
    ## https://ark.intel.com/content/www/us/en/ark/products/91767/intel-xeon-processor-e52650-v4-30m-cache-2-20-ghz.html
    batch = 105,
    ## brain/snowball Intel(R) Xeon(R) Gold 6240 CPU @ 2.60GHz
    ## https://www.intel.com/content/www/us/en/products/sku/192443/intel-xeon-gold-6240-processor-24-75m-cache-2-60-ghz.html
    snowball = 150
)

@@

elapsed_runtime <- sum(
    subset(tar_meta(), !type %in% c("function", "object", "branch"))$seconds
)

kgco2e <- tdp["snowball"] / 1000 * elapsed_runtime / 3600 * kgco2kwh
kgco2e

## Umweltbundesamt
## Ökologische Bewertung von Verkehrsarten
## Erscheinungsjahr August 2020, Autor(en): Michel Allekotte, Fabian Bergk, Kirsten Biemann, Carolin Deregowski, Wolfram Knörr, Hans-Jörg-Althaus, Daniel Sutter, Thomas Bergmann
## p. 214-215
## https://www.umweltbundesamt.de/sites/default/files/medien/479/publikationen/texte_156-2020_oekologische_bewertung_von_verkehrsarten_0.pdf
## Gesamt CO2eq (nur Verbrauch und Energiebereitstellung) je Personen km,
## A2, Tab. 69: PKW TTW 131 gCO2eq/Pkm, A3, Tab. 71.: PKW WTT 22 gCO2eq/Pkm
carkgco2e <- 153/ 1000
km <- kgco2e / carkgco2e
```

The calculations were conducted using the high performance computing (HPC)
cluster of the University Greifswald.
In 2018 the average carbon efficiency of the German power grid was
`r kgco2kwh` kgCO~2~eq/kWh [@icha2021].
A single run of the complete calculation pipeline took
`r sprintf("%.1f", elapsed_runtime / 3600)` hours of computation on an
Intel(R) Xeon(R) Gold 6240 CPU (thermal design power: 150 W).
The total estimated emissions were at least
`r sprintf("%.2f", kgco2e)` kgCO~2~eq
(ignoring development, test runs, etc.).
This is equivalent to `r sprintf("%.1f", km)` km driven by an average car
[@allekotte2021].

>>>>

```{r benchmark-plot, fig.cap = "Benchmark results of machine learning algorithms.", echo = FALSE}
r <- bmrk_results$clone()
id <- grep("^scale", x = r$learners$learner_id, invert = TRUE, value = TRUE)
r$filter(task_id = "zlog_eldd", learner_id = id)
autoplot(r) +
    geom_boxplot(aes(fill = learner_id)) +
    geom_jitter(position = position_jitter(0.2)) +
    scale_fill_viridis(discrete = TRUE) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

@@

```{r co2e, include = FALSE}
tdp <- c(
    ## brain/(batch|login) Intel(R) Xeon(R) CPU E5-2650 v4 @ 2.20GHz
    ## https://ark.intel.com/content/www/us/en/ark/products/91767/intel-xeon-processor-e52650-v4-30m-cache-2-20-ghz.html
    login = 105,
    ## brain/snowball Intel(R) Xeon(R) Gold 6240 CPU @ 2.60GHz
    ## https://www.intel.com/content/www/us/en/products/sku/192443/intel-xeon-gold-6240-processor-24-75m-cache-2-60-ghz.html
    ## TDP 150, contains 2 processors
    ## (but even with workers = 72, we barely use more than 36, so 150 instead of 300 W should be fine)
    snowball = 150
)

@@

tm <- tar_meta(fields = c("name", "type", "seconds"))
tm <- tm[tm$type %in% c("pattern", "stem"),]
tm$node <-
    ifelse(grepl("^boot|^bmrks$|^arcvob$", tm$name), "snowball", "login")

tm$runtime <- tm$seconds *
    ifelse(tm$node == "snowball", 32, 1) # on snowball we use 32 workers
kgco2e <- sum((tm$runtime / 3600) * (tdp[tm$node] / 1000)) * kgco2kwh
kgco2e

## Umweltbundesamt
## Ökologische Bewertung von Verkehrsarten
## Erscheinungsjahr August 2020, Autor(en): Michel Allekotte, Fabian Bergk, Kirsten Biemann, Carolin Deregowski, Wolfram Knörr, Hans-Jörg-Althaus, Daniel Sutter, Thomas Bergmann
## p. 214-215
## https://www.umweltbundesamt.de/sites/default/files/medien/479/publikationen/texte_156-2020_oekologische_bewertung_von_verkehrsarten_0.pdf
## Gesamt CO2eq (nur Verbrauch und Energiebereitstellung) je Personen km,
## A2, Tab. 69: PKW TTW 131 gCO2eq/Pkm, A3, Tab. 71.: PKW WTT 22 gCO2eq/Pkm
carkgco2e <- 153 / 1000
km <- kgco2e / carkgco2e
```

The calculations were conducted using the high performance computing (HPC)
cluster of the University Greifswald.
In 2018 the average carbon efficiency of the German power grid was
`r kgco2kwh` kgCO~2~eq/kWh [@icha2021].
A single run of the complete calculation pipeline took roughly
`r sprintf("%.1f", sum(tm$runtime) / 3600)` hours of computation on an
Intel(R) Xeon(R) E5-2650 v4 and
Intel(R) Xeon(R) Gold 6240 CPU (thermal design power: 105 and 150 W).
The total estimated emissions were at least
`r sprintf("%.2f", kgco2e)` kgCO~2~eq
(ignoring development, test runs, etc.).
This is equivalent to `r sprintf("%.1f", km)` km driven by an average car
[@allekotte2021].
